\documentclass[classic]{moderncv}

% moderncv styles
\moderncvstyle{casual}

% character encoding
%\usepackage[utf8]{inputenc}
\usepackage[french]{babel}
\usepackage[latin1]{inputenc}
% personal data
\firstname{Johan}
\familyname{Math\'e}
\title{Embedded/Networks Computer Engineer}
\address{5, rue Pasteur - 60200 Compiegne}
\phone{+33 6 85 03 35 35}
\email{johan.mathe@etu.utc.fr}
\extrainfo{{\small Driver license}}
%\renewcommand{\listsymbol}{{\fontencoding{U}\fontfamily{ding}\selectfont\tiny\symbol{'102}}}
\definecolor{see}{rgb}{0.5,0.5,0.5}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
\maketitle%
\makequote%
%
\section{In a nutshell}
\cvresume{Student in engineering at \textbf{Université de Technologie de Compiègne}, near from Paris, in France. Specialisation in computer science.}{Minor in philosophy of cultural digital communications.}
\cvresume{Specialisation in embedded systems \& information systems. Conscious of their current convergence}{Looking for problematics of contemporary world with travels and photography.}
%
\section{Studies}
\cventry{2007}{Engineering degree}{University of Waterloo}{Canada}{One term exchange}{Engineering and computer science}{}
\cventry{Since 2005}{Engineering degree}{Université de Technologie de Compiègne}{}{Computer science engineer degree}{Major embedded systems, netwoks and digital communications.}
\cventry{2003-2005}{DEUTEC}{Université de Technologie de Compiègne}{}{First degree for engineering preparation}{Scientific general culture.}
\cventry{2001-2003}{French baccalauréat}{Secondary school of Futuroscope}{French Baccalauréat with option in maths and in engineering.}{}{With distinction.}
%

\section{Employment history}
\cventry{Since 2006}{Information systems}{Musée national d'art moderne}{Paris}{France}{Design of a network achitecture and coding media analysis tools (C/C++)\newline{\itshape\color{see}\footnotesize{}See \httplink{www.iri.centrepompidou.fr}.}}

\cventry{2004-2006}{Electronic design \& code}{Heudyasic laboratory}{Compiegne}{France}{Design of motherboards for robots.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.auryon.utc.fr}.}}
%\cventry{Depuis 2004}{}{}{}{}{ Mise en place et présidence d'une association de gestion de l'informatique de toutes les associations étudiantes de l'utc  gestion du parc de serveurs des associations de l'université de technologie de Compiègne.}
\cventry{2005}{Webdesign}{Autofix}{Tampico}{Mexico}{One month in a Car company. Web coder and designer.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.autofix.com.mx}.}}
\cventry{2004}{Hotline}{U.T.C}{Compiègne}{France}{Helping students of the university using their Linux laptop.}
%\cventry{2003}{Prototypage}{Imtec Network Services}{}{}{Conception d'un prototype de Gestion de piscine au sein de la société IMTEC (Vienne).}
\cventry{2002}{Building information systems}{Imtec Network Services}{Poitiers}{France}{Installation of various servers (proxies, mail, web...). Teaching unix skills.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.imtec-group.com}.}}

\section{Clubs}
\cventry{2004-2005}{DGA micro-uav contest}{U.T.C}{Compiegne}{}{Design of the motherboards of an UAV for the French Army.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.auryon.utc.fr}.}}
\cventry{Since 2004}{Information systems design}{U.T.C}{Compiegne}{France}{Creation of a computer science club to help the others clubs of the university with the school network.\newline{\itshape\color{see}\footnotesize{}See \httplink{wwwassos.utc.fr/simde/}.}}
%

\section{Embedded system \& electronic skills}
\cvitem{\textbf{OS}}{Linux, QNX, microC/OS2, RTAI.}
\cvitem{\textbf{Langages}}{C/C++, ASM x86, ASM 68k.}
\cvitem{\textbf{Theory}}{VHDL,Scilab/Scicos, Matlab/Simulink, Petri Nets, Grafcet.}
\cvitem{\textbf{Digital Com.}}{I2C, CAN/VAN, Dallas 1 Wire, 802.3, 802.11}
\cvitem{\textbf{Electronics}}{Boards design : ORCAD, Eagle (has contributed).}
\cvitem{\textbf{RF electronics}}{Basic knoweldge for radio-frequency microelectronics : passive on-chip components on chip components}
\cvitem{\textbf{Signal analysus}}{Theoretical digital signal analysis.}
\cvitem{\textbf{Others}}{DSP, FPGA, Xscale, 68HCS12, Coldfire, PC104, PIC Microchip, ATMEL AVR.}
%

\section{Information systems}
\cvitem{\textbf{Coding languages}}{C, C++, PHP, Perl, CGI, Scripts shell (bash, zsh).}
\cvitem{\textbf{Document formatting}}{\LaTeX , Scribus}
\cvitem{\textbf{Unices}}{Using Linux since 1999. Sytem programming under Unix.}
\cvitem{\textbf{Distributions}}{Debian/Ubuntu expert \& very good knowledge of Gentoo/Slackware.}
\cvitem{\textbf{Internet servers}}{webservers (Apache), ftp, mailing-lists (mailman,sympa), proxy (Squid), dhcp, mail (postfix,exim), SMB, news, cups...}
\cvitem{\textbf{System}}{Metrology (rrdtools), IDS (snort).}
\cvitem{\textbf{Databases}}{SQL (MySQL, Postgre), LDAP (openLDAP).}

\section{Languages}
\cvlanguage{English}{Fluent}{Fisrt learnt language.\\Six months in North America (Canada-Ontario/Usa).}
\cvlanguage{Spanish}{Fluent}{Second learnt language.\\Passed four level at university.\\Three months in South America.}
\cvlanguage{Chineese}{Notions}{One course followed at university}
\cvlanguage{French}{Mothertongue}{}
%

\end{document}
